Is It Possible to Steal Money Through USB-C?

### 2020-12-20 WOOT/Files/related_work.tex
add related_work defense

>>>>

Tian, Jing, et al.[1] have made a brief overview of the defense countermeasures over four layers attack in the article. For attacks against human-layer problems, [2],[3]raise people's awareness of social engineering,[][][4],[5],[6] prevent the data from being stolen by on-device encryption, [7],[8] provide host authentication, [8]monitor data flow to record potential malicious IO behaviors and [9],[10]block physical connections to defense. In application layer,modification over OS and driver are adapted. [11],[12],[13] harden  host system to prevent automatic execution of malicious code. GOOD USB[14] offers strict access control, with the system soliciting desired functionality from the user and blocking other functionality for a device. Ghost[15] simulates as a USB device to detect if the host has malicious code injection. In transport layer,

FirmUSB[16] and VIPER[17] check the firmware of the device to ensure its safety. Fuzzing is a method of detecting vulnerabilities by providing unexpected input to the target system and monitoring for abnormal results. Some related work,[][][18],[19],[20] ,focuses on using USB fuzzing approach to detect potential bugs in USB driver. USBFirewall[21] protects the host based on error detection of USB communication packages. In some related work, [14],[22], e. g, VM is deployed in host to interact with the USB device for malicious behavior detection. In physical layer, some related work like [23] consider anti-fingerprinting ,and some others like [24] consider data encryption on USB bus.
